---
title: "EWM checks"
author: "Balint SZEBENYI"
date: '2016 december 1 '
output: html_document
---



```{r knitr_setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE, echo=FALSE}
PROJECT_DIR <- '/home/szebenyib/win7_link/projektek/2016_audi/ewm/'
knitr::opts_knit$set(root.dir = PROJECT_DIR)
options(java.parameters = "-Xmx4096m")
```

Loading necessary packages.

```{r load_packages, message=FALSE}
library(dplyr)
library(testthat)
library(lubridate)
library(stringr)
```

# Note

If this document could be generated, then all tests have passed.

# GH_EW_01

## Input reading

```{r read_data}
df <- read.csv(file = paste(PROJECT_DIR,
                     "result_package_gh_ew_01_mls.csv",
                     sep=""),
               header = TRUE,
               sep = ",",
               dec = ",")
df <- tbl_df(df)
```

Fixing column names.

```{r column_name_fix_1}
colnames(df) <- gsub("X.BIC.",
                     "",
                     colnames(df))
```

Fixing timestamps to have the correct format.

```{r timestamp_conversion_1}
colnames_to_ymd_convert <- grep("GEWTST",
                                colnames(df),
                                value = TRUE)

df <-df %>%
  mutate_each_(funs(ymd_hms),
               vars = colnames_to_ymd_convert)
# There will be warnings, since empty values cannot
# be parsed. Those will become NAs, which is ok.
```

## Checks

Checking which stat and tstp columns have their respective counterparts in gewtstp gewstat respectively. (All stat columns have their tstp counterpart and vice versa.)

```{r tstp_stat_checks}
colnames_gewstat_check <- grep("GEWSTAT",
                               colnames(df),
                               value = TRUE)
colnames_gewtstp_check <- grep("GEWTSTP",
                                colnames(df),
                                value = TRUE)
check_if_contained <- function(source, target_list) {
  # Comparing the numbers
  checker_list <- grepl(substr(source, 8, 10),
                        target_list)
  return(any(checker_list))
}
check_in_gewstat <- function(source) {
  return(check_if_contained(source,
                            colnames_gewstat_check))
}
check_in_gewtstp <- function(source) {
  return(check_if_contained(source,
                            colnames_gewtstp_check))
}
gewstats_in_gewtstp <- unlist(lapply(X = colnames_gewstat_check,
                                     FUN = check_in_gewtstp))
gewtstps_in_gewstat <- unlist(lapply(X = colnames_gewtstp_check,
                                     FUN = check_in_gewstat))
colnames_gewstat_check <- colnames_gewstat_check[gewstats_in_gewtstp]
colnames_gewtstp_check <- colnames_gewtstp_check[gewtstps_in_gewstat]
```

Checking that if there are values in the stat columns then the time stamps are not empty.

```{r tstp_stat_content_check}

stat_tstp_checker <- function(df, stat, tstp) {
  # If there is a stat value but NA in the timestamp field,
  # then it is a wrong row.
  wrong_rows_df <- df %>%
    filter_(as.formula(paste("~!is.na(",
                             as.name(stat),
                             ") & is.na(",
                             as.name(tstp),
                             ")",
                             sep = "")))
      # !is.na(as.name(stat)) & is.na(as.name(tstp)))
  return(wrong_rows_df)
}

for(i in 1:length(colnames_gewtstp_check)) {
  wrong_rows_df <- stat_tstp_checker(df,
                        colnames_gewstat_check[i],
                        colnames_gewtstp_check[i])
  test_that(desc = paste(i,
                         " - ",
                         colnames_gewtstp_check[i],
                         paste = ""),
            code = {expect_equal(object = nrow(wrong_rows_df),
                                     expected = 0)
    })
}
# If there are no errors all is good.
```

Checking that all KPIs that are LE relevant are calculated correctly.

```{r LE_checks}
le_tester <- function(df, later_tstp, earlier_tstp) {
  later_tstp_name <- as.name(paste("GEWTSTP",
                           later_tstp,
                           sep = ""))
  earlier_tstp_name <- as.name(paste("GEWTSTP",
                             earlier_tstp,
                             sep = ""))
  result_name_abap <- as.name(paste("GEW",
                       earlier_tstp,
                       later_tstp,
                       "L",
                       sep = ""))
  result_name_r <- paste(earlier_tstp,
                         later_tstp,
                         "L",
                         sep = "")
  a <- df %>%
    mutate_(result = as.formula(paste("~time_length((",
                           later_tstp_name,
                           "-",
                           earlier_tstp_name,
                           "), 'seconds') - ",
                           result_name_abap,
                           sep = ""))) %>%
    # Translates into:
    # mutate(result = time_length(("GEWTSTP30" - "GEWTSTP20"),
    #                          "seconds") - "GEW2030L") %>%
    filter(abs(result) > 0.01)
    # Minor differences may occur due to calculations and time_length
    # returning numeric and not integer, this is only a number
    # arithmetic phenomenon and not an error.
  if (nrow(a) != 0) {
    browser()
  } else {
    test_that(desc = result_name_r, code = {
                        expect_equal(object = nrow(a),
                                     expected = 0)
    })
  }
}
le_tester(df = df,
          later_tstp = 30,
          earlier_tstp = 20)
le_tester(df = df,
          later_tstp = 40,
          earlier_tstp = 30)
le_tester(df = df,
          later_tstp = 75,
          earlier_tstp = 65)
le_tester(df = df,
          later_tstp = 80,
          earlier_tstp = 70)
le_tester(df = df,
          later_tstp = 90,
          earlier_tstp = 80)
le_tester(df = df,
          later_tstp = 80,
          earlier_tstp = 20)
```

Checking that TEs calculated here and in BW match.

In case of TE calculations if min is to be calculated but there are NAs present in the records, then the minimum will not be calculated. If the minimum is not calculated, then the difference is also NA. Comparing 0s from SAP and NAs from R (0 - NA) will result in NAs and those are not selected by the dplyr filter statement.

Keep only the values where we have a TE

```{r}
dfx <- df %>% 
  filter(!is.na(G0WM_TU_N)) %>%
  arrange(G0WM_TU_N)
```

```{r TE_checks}
te_calcs <- dfx %>%
  group_by(G0WM_TU_N) %>%
  summarise(minGEWTSTP40 = min(GEWTSTP40),
            maxGEWTSTP45 = max(GEWTSTP45),
            avgGEWTSTP45 = mean(GEWTSTP45),
            minGEWTSTP65 = min(GEWTSTP65),
            maxGEWTSTP65 = max(GEWTSTP65),
            minGEWTSTP75 = min(GEWTSTP75),
            maxGEWTSTP75 = max(GEWTSTP75)) %>%
  mutate(calc4045T = maxGEWTSTP45 - minGEWTSTP40,
         calc6565T = maxGEWTSTP65 - minGEWTSTP65,
         calc7575T = maxGEWTSTP75 - minGEWTSTP75)
dfx <- left_join(dfx, te_calcs,
                 by = "G0WM_TU_N")
rm("te_calcs")

te_tester <- function(df, later_tstp, earlier_tstp) {
  calc_tstp_name <- as.name(paste("calc",
                           earlier_tstp,
                           later_tstp,
                           "T",
                           sep = ""))
  result_name_abap <- as.name(paste("GEW",
                       earlier_tstp,
                       later_tstp,
                       "T",
                       sep = ""))
  result_name_r <- paste(earlier_tstp,
                         later_tstp,
                         "T",
                         sep = "")
  a <- dfx %>%
    mutate_(result = as.formula(paste("~",
                                      calc_tstp_name,
                                      "-",
                                      result_name_abap,
                                      sep = ""))) %>%
    filter(abs(result) > 0.01)
  test_that(desc = calc_tstp_name, code = {
    expect_equal(object = nrow(a),
                 expected = 0)
  })
}

te_tester(df = dfx,
          later_tstp = 45,
          earlier_tstp = 40)
te_tester(df = dfx,
          later_tstp = 65,
          earlier_tstp = 65)
te_tester(df = dfx,
          later_tstp = 75,
          earlier_tstp = 75)
```

Checking that the TE's last timestamps GEWTSTXXL get filled for later TE calcs in BW.

```{r TE check that relevant GEWTSTXXL gets filled}
te_gewtstxxl_tester <- function(df, later_tstp) {
  last_name_r <- paste("maxGEWTSTP",
                       later_tstp,
                       sep = "")
  last_name_abap <- as.name(paste("GEWTST",
                          later_tstp,
                          "L",
                          sep = ""))
  a <- df %>% mutate_(result = as.formula(paste("~",
                                                last_name_r,
                                                "-",
                                                last_name_abap))) %>%
              filter(abs(result) > 0)
  test_that(desc = "The relevant gewtstXXl last time stamps are filled for TE calcs later",
            code = expect_equal(object = nrow(a),
                                expected = 0))
}

te_gewtstxxl_tester(df = dfx,
                    later_tstp = 45)
te_gewtstxxl_tester(df = dfx,
                    later_tstp = 65)
te_gewtstxxl_tester(df = dfx,
                    later_tstp = 75)
```

```{r export}
write.csv(x = dfx,
          file = "dfx.csv")
```

# GH_EW_B02 from GH_EW_01

## Input reading

Reading the following input files:
* source package from GH_EW_01 to GH_EW_B02
* result package from GH_EW_01 to GH_EW_B02
* mapping (in_out_df, log table)
* setup table (bic_pgewkpi)

```{r read_data2}
source_df <- read.csv(file = paste(PROJECT_DIR,
                     "source_package_gh_ew_b02.csv",
                     sep=""),
               header = TRUE,
               sep = ",",
               dec = ",",
               stringsAsFactors = FALSE)
source_df <- tbl_df(source_df)
result_df <- read.csv(file = paste(PROJECT_DIR,
                     "result_package_gh_ew_b02.csv",
                     sep=""),
               header = TRUE,
               sep = ",",
               dec = ",",
               stringsAsFactors = FALSE)
result_df <- tbl_df(result_df)
in_out_df <- read.csv(file = paste(PROJECT_DIR,
                     "records_in_out_gh_ew_b02.csv",
                     sep=""),
               header = TRUE,
               sep = ",",
               dec = ",")
in_out_df <- tbl_df(in_out_df)
bic_pgewkpi <- read.csv(file = paste(PROJECT_DIR,
                       "bic_pgewkpi.csv",
                       sep=""),
               header = TRUE,
               sep = ",",
               dec = ",",
               stringsAsFactors = FALSE)
bic_pgewkpi <- tbl_df(bic_pgewkpi)
```

Removing unnecessary part from column names.

```{r column_name_fix_2}
colnames(source_df) <- gsub("X.BIC.",
                            "",
                            colnames(source_df))
colnames(result_df) <- gsub("X.BIC.",
                            "",
                            colnames(result_df))
colnames(bic_pgewkpi) <- gsub("X.BIC.",
                              "",
                              colnames(bic_pgewkpi))
```

Fixing timestamp's format.

```{r timestamp_conversion_2}
colnames_to_ymd_convert <- grep("GEWTSTP",
                                colnames(source_df),
                                value = TRUE)

source_df <- source_df %>%
  mutate_each_(funs(ymd_hms),
               vars = colnames_to_ymd_convert)

colnames_to_ymd_convert <- c("CALDAY")
result_df <- result_df %>%
  mutate_each_(funs(ymd),
               vars = colnames_to_ymd_convert)
# There will be warnings, since empty values cannot
# be parsed. Those will become NAs, which is ok.
```

## Checks

Check that relevant KPIs are generated.

```{r result_row_fetcher}
get_result_rows <- function(source_rows) {
  in_out_rows <- in_out_df %>%
    filter(INRECORD %in% source_rows$INDEX)

  result_rows <- result_df %>%
    filter(INDEX %in% in_out_rows$OUTRECORD)
  
  return(result_rows)
}
```

Checking logger, in_out_mapping for TEs.

Checking that the mapping via TE (G0WM_TU_N) is the same as the mapping via in_out values of the transformation logger. **This way the logger can be checked to be working well.** There might be some records which do not have a TE yet, these have to be filtered out from the check, these are in the state before they could have received that TE number.

```{r checking_in_out_mapping_via_TE}
source_rows <- source_df %>%
  filter(!is.na(G0WM_TU_N))

result_rows_via_mapping <- get_result_rows(source_rows)

result_rows_via_g0wm_tu_n <- result_df %>%
  filter(G0WM_TU_N %in% source_rows$G0WM_TU_N)

test_that(desc = "G0WM_TU_N mapping is the same as the logger mapping",
          code = {
            expect_true(nrow(result_rows_via_mapping) ==
                        nrow(result_rows_via_g0wm_tu_n))
          })
rm("source_rows",
   "result_rows_via_mapping",
   "result_rows_via_g0wm_tu_n")
```

Checking a single KPI, KPI3.

KPI3 has to be generated only, as tstp20 and tstp30 are the only present values. This is the case for rows where there is not LE given (no G0WM_TU_N). The identification is therefore possible only via in-out mapping of the transformation logger. In such a case only one record should be found in the result row, that is to be checked as well.

```{r single_kpi}
source_rows <- source_df %>%
  filter(!is.na(GEWTSTP20) &
        !is.na(GEWTSTP30) &
        is.na(GEWSTAT40))

result_rows <- get_result_rows(source_rows)

test_that(desc = "Only one result is created for records with max GEWTSTP30",
          code = {
            expect_true(nrow(source_rows) == nrow(result_rows))
          })

test_that(desc = "Only KPI3 got generated and nothing else for records with max GEWTSTP30",
          code = {
            expect_true(all(result_rows$GEWKPI == "KPI3"))
          })
rm("source_rows",
   "result_rows")
```

Checking KPI4.

Checking that if KPI4 is present then KPI3 is present as well. Besides checking that if KPI4 is present then TE (G0WM_TU_N) is not empty.

```{r KPI3_KPI4}
source_rows <- source_df %>%
  filter(!is.na(GEWTSTP40))

result_rows <- get_result_rows(source_rows)

test_that(desc = "KPI3 is present if KPI4 exists",
          code = {
            a <- result_rows %>%
              filter(GEWKPI == "KPI3")
            b <- result_rows %>%
              filter(GEWKPI == "KPI4")
            expect_true(nrow(a) == nrow(b))
          })

test_that(desc = "TE (G0WM_TU_N) is not empty if KPI4 is present",
          code = {
            a <- result_rows %>%
              filter(GEWKPI == "KPI4" &
                    is.na(G0WM_TU_N))
            expect_true(nrow(a) == 0)
          })

rm("source_rows",
   "result_rows")
```

Check that exactly the necessary amount of KPIs got generated globally. (The number of result rows should be equal to the number that we expect to see.)

```{r KPI_number_check}
count_non_zero <- function(colname) {
  return(sum(source_df[colname] != 0,
             na.rm = TRUE))
}

to_become_KPI_columns <- grep(pattern = "^GEW[0-9]{4}[LT]$",
                              x = colnames(source_df),
                              value = TRUE)
a <- bic_pgewkpi %>%
  filter(GEWKPITYP == "ST") %>%
  select(GEWSTAT)
strip_bic <- function(name) {
  substr(x = name,
         start = 6,
         stop = nchar(name))
}
a <- lapply(X = unlist(a),
       FUN = strip_bic)
to_become_KPI_columns <- c(to_become_KPI_columns,
                           unlist(a))

KPIs_to_be_generated <- unlist(lapply(X = to_become_KPI_columns,
       FUN = count_non_zero))

kpi_gen <- as.data.frame(to_become_KPI_columns,
                         stringsAsFactors = FALSE)
kpi_gen <- cbind(kpi_gen, KPIs_to_be_generated)

bic_pgewkpi <- bic_pgewkpi %>%
  mutate(to_become_KPI_columns = ifelse(GEWKPITYP == "LE" |
                                        GEWKPITYP == "TE" ,
                                        yes = paste("GEW",
                                                     substr(bic_pgewkpi$GEWVONST, 13, 14),
                                                     substr(bic_pgewkpi$GEWBISST, 13, 14),
                                                     substr(bic_pgewkpi$GEWKPITYP, 1, 1),
                                                     sep = ""),
                                        no = ifelse(GEWKPITYP == "ST",
                                                    yes = strip_bic(GEWSTAT),
                                                    no = NA)
                                        )
         ) %>%
  filter(OBJVERS == "A" & GEWKPI != "")
kpi_gen <- left_join(x = kpi_gen,
                     y = bic_pgewkpi,
                     by = "to_become_KPI_columns")

kpi_gen$KPIs_to_be_generated = as.numeric(kpi_gen$KPIs_to_be_generated)

test_that(desc = paste("The number of KPIs to be generated equals",
                       "to the number of rows in the result package",
                       sep = ""),
          code = {
            expect_true(sum(kpi_gen$KPIs_to_be_generated) ==
                        nrow(result_df))
          })
rm("a")
```

Checking that the necessary number of rows have been generated per KPI.

```{r KPI_number_check_2}
count_KPI <- function(KPI) {
  a <- result_df %>%
   filter(GEWKPI == KPI)
  return(nrow(a))
}

a <- unlist(lapply(X = kpi_gen$GEWKPI,
            FUN = count_KPI))

kpi_gen <- kpi_gen %>%
  mutate(KPIs_actually_generated = a)

test_that(desc = "KPI generation numbers per KPI matches with expectations",
          code = {
            expect_equal(object = kpi_gen$KPIs_actually_generated,
                         expected =  kpi_gen$KPIs_to_be_generated)
          })
rm("a")
```

Checking that the caldays are generated from the right source.

Cases:
* LE KPI -> Bisdatum
* TE KPI -> TE's last bisdatum

```{r check_that_caldays_are_generated_from_the_right_source}
LE_KPIs <- bic_pgewkpi %>%
  filter(GEWKPITYP == "LE")
TE_KPIs <- bic_pgewkpi %>%
  filter(GEWKPITYP == "TE")
ST_KPIs <- bic_pgewkpi %>%
  filter(GEWKPITYP == "ST")

a <- result_df %>%
  filter(GEWKPI %in% LE_KPIs$GEWKPI) %>%
  filter(GEWBISD != CALDAY)

test_that(desc = "All LE KPIS have the same calday as the bisdatum",
          code = expect_equal(nrow(a),
                              object = 0))

a <- result_df %>%
  filter(GEWKPI %in% TE_KPIs$GEWKPI)
a <-left_join(x = a,
              y = in_out_df,
              by = c("INDEX" = "OUTRECORD")) %>%
    select(-INDEX.y)
a <- left_join(x = a,
               y = source_df,
               by = c("INRECORD" = "INDEX")) %>%
    select(-RECORD.y)
a <- left_join(x = a,
               y = bic_pgewkpi,
               by = "GEWKPI")


a <- a %>% mutate(to_become_last = paste("GEWTST",
                                         substr(x = GEWBISST,
                                               start = 13,
                                               stop = 14),
                                         "L",
                                         sep = ""))
colnames_to_ymd_convert <- grep("^GEWTST[0-9]{2}L$",
                                colnames(source_df),
                                value = TRUE)

a <- a %>%
  mutate_each_(funs(ymd_hms),
               vars = colnames_to_ymd_convert) %>%
  mutate_each_(funs(date),
               vars = colnames_to_ymd_convert)
#Warnings about X failed to parse are OK.

calc_tst_delta <- function(row) {
  col_to_lookup <- row["to_become_last"][[1]]
  as.numeric(difftime(row["CALDAY.x"],
                      row[col_to_lookup]))
}
deltas <- apply(X = a,
                 MARGIN = 1,
                 FUN = calc_tst_delta)
#Some deltas are possible due to UTC vs Budapest, checking
#that this is indeed the case
a_where_delta_bigger_0 <- a[deltas > 0, ]
a_relevant_gewtstp45 <- a %>%
  filter(INDEX.x %in% a_where_delta_bigger_0$INDEX.x) %>%
  select(GEWTSTP45)
#Timestamps are stored 
a_relevant_gewtstp45_recalc_budapest <- with_tz(a_relevant_gewtstp45,
                                                tzone="Europe/Budapest")
within_an_hour_after_midnight <- sum(hour(a_relevant_gewtstp45_recalc_budapest$GEWTSTP45) + 1)
test_that(desc = paste("The difference between the relevant GEWTSTXXL field",
                       "and the calday is not zero everywhere and not because of",
                       "timezone difference"),
          code = expect_equal(sum(deltas) - within_an_hour_after_midnight, 0))
rm("a", "a_relevant_gewtstp45_recalc_budapest",
   "a_relevant_gewtstp45", "a_where_delta_bigger_0")
  
```

# GH_EW_B02 from DS05

## Reading data

```{r ds05_import}
ds05 <- read.csv(file = paste(PROJECT_DIR,
                     "0wm_ds05_samplerecords.txt",
                     sep=""),
               header = TRUE,
               sep = "\t",
               dec = ",",
               stringsAsFactors = FALSE,
               encoding = "latin1")
ds05 <- tbl_df(ds05)

ds05 <- ds05 %>%
  mutate_each_(funs(ymd_hms),
               vars = c("Quittierung", "X0WM_CREA_AT",
                        "Anfangsdatum", "Wareneingang"))
```

Keeping only the necessary columns.

```{r experiment}

df <- ds05 %>%
  arrange(Von.Handling.Unit, Quittierung)
df <- df %>% select(-X, -AME, -Charge, -X0WM_COO, -X0WM_DRSRC,
   -Belegtyp, -...INDOCNO, -Prüfart, -...MAT_GRP, -X0WM_NLBER,
   X0WM_NPTYP, -X0WM_PRCES, -X0WM_PRIO, -...PTWYINV,
   -Belegtyp.1, -X0WM_QDOCNO, -...RDOCCAT, 
   -Belegnummer.der.Belegreferenz, -X0WM_RITMNO, -Sicht,
   -X0WM_SRSRC, -...SSTROLE, -Von.TE, -X0WM_ST_USE,
   -X0WM_TOSTAT, -X0WM_TRART, -...TSTROLE, -X0WM_UNIT_T,
   -X0WM_UNIT_V, -X0WM_UNIT_W, -X0WM_VALUOM, -X0WM_VAS,
   -...VFDA_TS, -X0WM_VLBER, -Welle, -...WAVE_IT, -X0WM_CAPA)
df <- df %>% select(Von.Handling.Unit, Nach.Handling.Unit, X0WM_MATNR, X0WM_VLTYP, X0WM_NLTYP, Prozess, Quittierung, Queue, Wareneingang, X0WM_WHO, X0WM_TANUM)
```